% -*- root: ../project.tex -*-

\section{Data} % (fold)
\label{sec:data}
\subsection{Results from numerical solution of the differential flow equation} % (fold)
\label{sub:results_from_numerical_solution_of_the_differential_flow_equation}
Results from solution of the differential flow equation for $M=10$. The first row contains the indexes in the horizontal direction. The producer is found in the lower-left corner; the injector is found in the upper-right corner.

{\tiny
\vspace{.5cm}
\hspace{-1cm}
\pgfplotstabletypeset[header=false, sci, sci sep align, sci zerofill]{../../results/peaceman/10x10-pressure.dat}}
% subsection results_from_numerical_solution_of_the_differential_flow_equation (end)

\subsection{Results from simulation using MRST} % (fold)
\label{sub:results_from_simulation_using_mrst}
Results from simulation using the Sintef MRST reservoir simulator. The first row contains the indexes in the horizontal direction. The producer is found in the lower-left corner; the injector is found in the upper-right corner.

{\tiny
\vspace{.5cm}
\hspace{-1cm}
\pgfplotstabletypeset[header=false, sci, sci sep align, sci zerofill]{../../results/mrst/11x11-pressure.dat}}
% subsection results_from_simulation_using_mrst (end)

\subsection{Results from simulation using ECL100 (metric)} % (fold)
\label{sub:results_from_simulation_using_ecl100_metric}
Results from simulation using the Schlumberger ECL100 reservoir simulator with metric units. The first row contains the indexes in the horizontal direction. The producer is found in the lower-left corner; the injector is found in the upper-right corner.

{\tiny
\vspace{.5cm}
\hspace{-1cm}
\pgfplotstabletypeset[header=false, sci, sci sep align, sci zerofill]{../../results/eclipse/11x11-pressure.dat}}
% subsection results_from_simulation_using_ecl100_metric (end)

\subsection{Results from simulation using ECL100 (lab)} % (fold)
\label{sub:results_from_simulation_using_ecl100_lab}
Results from simulation using the Schlumberger ECL100 reservoir simulator with lab units. The first row contains the indexes in the horizontal direction. The producer is found in the lower-left corner; the injector is found in the upper-right corner.

{\tiny
\vspace{.5cm}
\hspace{-1cm}
\pgfplotstabletypeset[header=false, sci, sci sep align, sci zerofill]{../../results/eclipse/11x11-pressure-lab.dat}}
% subsection results_from_simulation_using_ecl100_lab (end)

% section data (end)
